---
title: "Inferential statistics of the experimental data reported in *Neglect-Zero effects in the interpretation of quantifiers and disjunction*"
author: "Oliver Bott, Fabian Schlotterbeck, Tomasz Klochowicz, Sonia Ramotowska & Maria Aloni"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(cli)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(trimr)
library(lme4)
library(lmerTest)
library(sjPlot)
library(dplyr)
library(ggbreak)
library(Rmisc)
library(reshape2)
library(stringr)
library(rlang)
library(naniar)
library(LMERConvenienceFunctions)
library(betareg)
library(performance)
library(forcats)
```

```{r load data,include=FALSE}
load("trimmedData.RData")
```

# GLMER analysis of responses

Responses analyzed in two separate GLMER analyses:
1. Logit mixed-effects regression analysis of *weird question* vs. logically correct/incorrect answers (including all judgments provided within time limit)
2. Logit mixed-effects regression analysis of correct vs. incorrect answers (excluding *weird question* responses)

Both analyses conducted with Helmert coding of factor SIMPLIFIED MODEL (factor simplified from originally (up to) four levels to three levels: 1) psp violation, 2) empty set model, 3) control conditions), contrasts specified as follows:
1. psp violation vs. rest
2. empty set condition vs control conditions

Other fixed effects included for ES-quantifier experiment: MONOTONICITY (UP vs. DOWN) and QUANTIFIER TYPE (ARIS(totelian) vs. COMP(arative)); both contrasts were sum coded. 

```{r}
# code given responses in two binary dependent variables: 1) psp violation (yes vs. no), 
# 2) yes vs. no response, in case no psp violation occurred 
trimmed_data_esq$psp_violation <- case_when(trimmed_data_esq$given_response %in% c("komische Frage")
                                            ~ 1,
                                            trimmed_data_esq$given_response %in% c("ja, stimmt", 
                                                                                   "nein, stimmt nicht") 
                                            ~ 0)

trimmed_data_esq$yes_no <- case_when(trimmed_data_esq$given_response %in% c("ja, stimmt")
                                            ~ 1,
                                            trimmed_data_esq$given_response %in% c("nein, stimmt nicht") 
                                            ~ 0)

trimmed_data_esq$simp_model <- case_when(trimmed_data_esq$model %in% c("psp")
                                            ~ "psp",
                                            trimmed_data_esq$model %in% c("empty_set") 
                                            ~ "empty",
                                          trimmed_data_esq$model %in% c("true", "false") 
                                            ~ "control")

trimmed_data_esq$simp_model <- as.factor(trimmed_data_esq$simp_model)
trimmed_data_esq$mono <- as.factor(trimmed_data_esq$mono)
trimmed_data_esq$q_type <- as.factor(trimmed_data_esq$q_type)
levels(trimmed_data_esq$simp_model)
levels(trimmed_data_esq$simp_model)
levels(trimmed_data_esq$simp_model)
# Helmert coding of models (simp_model): contrast 1) psp vs. rest, 2) empty set vs. controls

myhelmert = matrix(c(-1/3, -1/3, 2/3, .5, -.5, 0), ncol = 2)
myhelmert


contrasts(trimmed_data_esq$simp_model) = myhelmert
contrasts(trimmed_data_esq$mono) = contr.sum(2)
contrasts(trimmed_data_esq$q_type) = contr.sum(2)

# analysis of psp violations in a logit mixed effects analysis



esq_psp_m1.0 <- glmer(psp_violation ~ 1 + 
                      mono *simp_model * q_type + 
                              (1|id) + 
                              (1+simp_model|scenario), 
                            data = trimmed_data_esq, 
                            family = binomial(link = "logit"),
                            glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=10^7)))

esq_psp_m1.1 <- update(esq_psp_m1.0, .~.-(1+simp_model|scenario)+(1|scenario))

anova(esq_psp_m1.1, esq_psp_m1.0)

#no convergence
#esq_psp_m1.1.1 <- update(esq_psp_m1, .~.-(1|scenario)+(1|item))
#anova(esq_psp_m1.1, esq_psp_m1.1.1)

#...

summary(esq_psp_m1.1) #sign. effect of simp_model1 

###################################################################################################################################
#### commented out: stepwise determination of random effects structure; only final model computed; leaving out by-item slopes #####
###################################################################################################################################

# ToDo: resolve interaction second contrast of simp_model x quant_type (probably due to greater difference between es and control for comparative qs)

# analysis of yes vs. no responses in a logit mixed effects analysis



# esq_acc_m1.0 <- glmer(accuracy ~ 1 + 
#                     mono *simp_model * q_type + 
#                              (1+simp_model*mono|id) + 
#                              (1|scenario), 
#                            data = trimmed_data_esq, 
#                            family = binomial(link = "logit"),
#                    glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=10^6)))


# esq_acc_m1.1 <- update(esq_acc_m1.0, .~.-(1+simp_model*mono|scenario)+(1+simp_model+mono|scenario))

# anova(esq_acc_m1.1,esq_acc_m1.0)

# esq_acc_m1.2 <- update(update(esq_acc_m1.1, .~.-(1+simp_model+mono|scenario)+(1+simp_model|scenario)))

# anova(esq_acc_m1.1,esq_acc_m1.2)

# esq_acc_m1.3 <- update(esq_acc_m1.2, .~.-(1+simp_model|scenario)+(1|scenario))

# anova(esq_acc_m1.3,esq_acc_m1.2)

# esq_acc_m1.4 <- update(esq_acc_m1.3, .~.-(1|scenario)+(1|item))

# anova(esq_acc_m1.3,esq_acc_m1.4)

# esq_acc_m1.5 <- update(esq_acc_m1.4, .~.-(1|item))

# anova(esq_acc_m1.5,esq_acc_m1.4)

# esq_acc_m1.6 <- update(esq_acc_m1.4, .~.-(1|item)+(1+simp_model|item))

# anova(esq_acc_m1.6,esq_acc_m1.4)

# esq_acc_m1.7 <- update(esq_acc_m1.6, .~.-(1+simp_model|item)+(1+simp_model+mono|item))

# anova(esq_acc_m1.6,esq_acc_m1.7)

# esq_acc_m1.8 <- update(esq_acc_m1.7, .~.-(1+simp_model+mono|item)+(1+simp_model*mono|item))

# anova(esq_acc_m1.8,esq_acc_m1.7)
 
 esq_acc_m1.4 <- glmer(accuracy ~ 1 + 
                     mono *simp_model * q_type + 
                              (1+simp_model*mono|id) + 
                              (1|item), 
                            data = trimmed_data_esq, 
                            family = binomial(link = "logit"),
                    glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=10^6)))

summary(esq_acc_m1.4)

#save(esq_acc_m1.8,esq_psp_m1.1,file="glmer_esq.RData")

trimmed_data_esq_aris <- subset(trimmed_data_esq, trimmed_data_esq$q_type=="aristotelean")
trimmed_data_esq_comp <- subset(trimmed_data_esq, trimmed_data_esq$q_type=="comparative")

esq_aris_acc_m1.0 <- glmer(accuracy ~ 1 + 
                      mono *simp_model + 
                              (1+simp_model*mono|id) + 
                              (1|item), 
                            data = trimmed_data_esq_aris, 
                            family = binomial(link = "logit"),
                    glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=10^6)))
summary(esq_aris_acc_m1.0)

esq_comp_acc_m1.0 <- glmer(accuracy ~ 1 + 
                      mono *simp_model + 
                              (1+simp_model*mono|id) + 
                              (1|item), 
                            data = trimmed_data_esq_comp, 
                            family = binomial(link = "logit"),
                    glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=10^6)))
summary(esq_comp_acc_m1.0)

#save(esq_acc_m1.8,esq_psp_m1.1,esq_aris_acc_m1.0,esq_comp_acc_m1.0,
     #file="glmer_esq.RData")

```

*Distributivity* experiment only employed the factor MODEL. Contrasts coded as above.

```{r}
#Distributivity
# code given responses in two binary dependent variables: 1) psp violation (yes vs. no), 
# 2) yes vs. no response, in case no psp violation occurred 
trimmed_data_fc$psp_violation <- case_when(trimmed_data_fc$given_response %in% c("komische Frage")
                                            ~ 1,
                                            trimmed_data_fc$given_response %in% c("ja, stimmt", 
                                                                                   "nein, stimmt nicht") 
                                            ~ 0)

trimmed_data_fc$yes_no <- case_when(trimmed_data_fc$given_response %in% c("ja, stimmt")
                                            ~ 1,
                                            trimmed_data_fc$given_response %in% c("nein, stimmt nicht") 
                                            ~ 0)

trimmed_data_fc$simp_model <- case_when(trimmed_data_fc$model %in% c("psp")
                                            ~ "psp",
                                            trimmed_data_fc$model %in% c("empty_set") 
                                            ~ "empty",
                                          trimmed_data_fc$model %in% c("true", "false") 
                                            ~ "control")

# Helmert coding of models (simp_model): contrast 1) psp vs. rest, 2) empty vs. controls

myhelmert = matrix(c(-1/3, -1/3, 2/3, .5, -.5, 0), ncol = 2)

trimmed_data_fc$simp_model <- as.factor(trimmed_data_fc$simp_model)
levels(trimmed_data_fc$simp_model)
contrasts(trimmed_data_fc$simp_model) = myhelmert



fc_psp_m1.0 <- glmer(psp_violation ~ 1 + 
                              simp_model + 
                              (1|id) + 
                              (1|scenario), 
                            data = trimmed_data_fc, 
                            family = binomial(link = "logit"),
                            glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=10^7)))

summary(fc_psp_m1.0)

trimmed_data_fc_wo_psp <- subset(trimmed_data_fc, trimmed_data_fc$model != "psp")

fc_acc_m1.0 <- glmer(yes_no ~ 1 + 
                              model + 
                              (1+model|id) + 
                              (1+model|item), 
                            data = trimmed_data_fc_wo_psp, 
                            family = binomial(link = "logit"),
                    glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=10^6)))
summary(fc_acc_m1.0)

save(esq_acc_m1.4,esq_psp_m1.1,esq_aris_acc_m1.0,esq_comp_acc_m1.0,fc_psp_m1.0,fc_acc_m1.0,
     file="glmer_esq_new.RData")

```

#acc in scalar implicature experiment

Simpler design. Just two models, no psp violation. Conduct single GLMER analysis comparing number of logical answers (i.e. *yes* responses) vs. "pragmatic" responses (*no* responses) for treatment coded contrast of model (base level: *implicature*; vs. *literal*). 

```{r}
#scalar implicature
# code given responses in one binary dependent variable: 1) yes vs. no response ignoring "weird" question responses


trimmed_data_si$yes_no <- case_when(trimmed_data_si$given_response %in% c("ja, stimmt")
                                            ~ 1,
                                            trimmed_data_si$given_response %in% c("nein, stimmt nicht") 
                                            ~ 0)

si_acc_m1.0 <- glmer(yes_no ~ 1 + 
                              model + 
                              (1|id) +
                              (1|item), 
                            data = trimmed_data_si, 
                            family = binomial(link = "logit"),
                    glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=10^6)))
summary(si_acc_m1.0)

si_acc_m1.1 <- glmer(yes_no ~ 1  + 
                              (1|id) +
                              (1|item), 
                            data = trimmed_data_si, 
                            family = binomial(link = "logit"),
                    glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=10^6)))
anova(si_acc_m1.0,si_acc_m1.1)

save(esq_acc_m1.4,esq_psp_m1.1,esq_aris_acc_m1.0,esq_comp_acc_m1.0,fc_psp_m1.0,fc_acc_m1.0,si_acc_m1.0,
     file="glmer_esq_new.RData")

# sign. difference between models
```


#RT in Empty-Set Quantifiers

Analyze RT data in LMER analyses ignoring PSP violations. Helmert contrast coding for COMP: 1) empty set model vs. controls, 2) small vs. large controls. The latter contrast is used to study MONOTONICITY x POLARITY interaction, the former contrast is used to study empty-set effects in RT. 

```{r}
trimmed_data_esq$yes_no <- as.factor(trimmed_data_esq$yes_no)

trimmed_data_esq_wo_psp <- subset(trimmed_data_esq, trimmed_data_esq$model != "psp")

trimmed_data_esq_wo_psp_comp <- subset(trimmed_data_esq_wo_psp, trimmed_data_esq_wo_psp$q_type == "comparative")

trimmed_data_esq_wo_psp_aris <- subset(trimmed_data_esq_wo_psp, trimmed_data_esq_wo_psp$q_type == "aristotelean")


#contrast
rt_esq_helmert = matrix(c(2/3, -1/3, -1/3, 0, .5, -.5), ncol = 2)
#comp
trimmed_data_esq_wo_psp_comp$model <- as.factor(trimmed_data_esq_wo_psp_comp$model)
contrasts(trimmed_data_esq_wo_psp_comp$model) = rt_esq_helmert
#aris
trimmed_data_esq_wo_psp_aris$model <- as.factor(trimmed_data_esq_wo_psp_aris$model)
contrasts(trimmed_data_esq_wo_psp_aris$model) = rt_esq_helmert


lmer_esq_comp.0 <- lmer(pictureRT ~ model*mono*yes_no+
       (1|id)+
       (1|item),
     data = trimmed_data_esq_wo_psp_comp,
     REML = FALSE)

summary(lmer_esq_comp.0)


lmer_esq_aris.0 <- lmer(pictureRT ~ simp_model*mono+yes_no+
       (1|id)+
       (1|item),
     data = trimmed_data_esq_wo_psp_aris,
     REML = FALSE)
#Warning can be ignored here

summary(lmer_esq_aris.0)

lmer_esq.0 <- lmer(pictureRT ~ q_type*simp_model*mono+yes_no+
       (1|id)+
       (1|item),
     data = trimmed_data_esq_wo_psp,
     REML = FALSE)
#Warning can be ignored here

summary(lmer_esq.0)

save(esq_acc_m1.4,esq_psp_m1.1,esq_aris_acc_m1.0,esq_comp_acc_m1.0,fc_psp_m1.0,fc_acc_m1.0,si_acc_m1.0,lmer_esq_comp.0, lmer_esq_aris.0,
     lmer_esq.0,
     file="glmer_esq_new.RData")
```

# RT in Distributivity Experiment 


```{r}
trimmed_data_fc$yes_no <- case_when(trimmed_data_fc$given_response %in% c("ja, stimmt")
                                            ~ 1,
                                            trimmed_data_fc$given_response %in% c("nein, stimmt nicht") 
                                            ~ 0)

trimmed_data_fc_wo_psp <- subset(trimmed_data_fc, trimmed_data_fc$model != "psp")

trimmed_data_fc_wo_psp$yes_no <- as.factor(trimmed_data_fc_wo_psp$yes_no)
trimmed_data_fc_wo_psp$model <- as.factor(trimmed_data_fc_wo_psp$model)
# contr.treatment(trimmed_data_fc_wo_psp$model, base = "empty_set")


lmer_fc.0 <- lmer(pictureRT ~ model * yes_no +
                    (1|id) +
                    (1|item), 
                  data = trimmed_data_fc_wo_psp,
                  REML = FALSE)

summary(lmer_fc.0)

lmer_fc.1 <- update(lmer_fc.0, .~. - model:yes_no)

anova(lmer_fc.1,lmer_fc.0)

lmer_fc.2 <- update(lmer_fc.1, .~. - model)

anova(lmer_fc.1,lmer_fc.2)

summary(lmer_fc.1)

# test for answer polarity effect in zero models

trimmed_data_fc_wo_psp_only_zero_model <- subset(trimmed_data_fc_wo_psp, trimmed_data_fc_wo_psp$model == "empty_set")

lmer_fc_zero_model.0 <- lmer(pictureRT ~ yes_no +
                    (1+yes_no|id) +
                    (1+yes_no|item), 
                  data = trimmed_data_fc_wo_psp_only_zero_model,
                  REML = FALSE)

summary(lmer_fc_zero_model.0)

lmer_fc_zero_model.1 <- lmer(pictureRT ~ 1 +
                    (1+yes_no|id) +
                    (1+yes_no|item), 
                  data = trimmed_data_fc_wo_psp_only_zero_model,
                  REML = FALSE)

anova(lmer_fc_zero_model.0,lmer_fc_zero_model.1)

# sign.; neglect-zero responses take longer than classical logical responses 
```

#RT in Scalar Implicature

```{r}
trimmed_data_si$yes_no <- case_when(trimmed_data_si$given_response %in% c("ja, stimmt")
                                            ~ 1,
                                            trimmed_data_si$given_response %in% c("nein, stimmt nicht") 
                                            ~ 0)

trimmed_data_si$yes_no <- as.factor(trimmed_data_si$yes_no)

trimmed_data_si_only_literal <- subset(trimmed_data_si, trimmed_data_si$model == "literal")

# answer polarity effect in "imp: false; lit: true" models: pragmatic responses take longer than classical logical responses

lmer_si.0 <- lmer(pictureRT ~ yes_no +
                    (1+yes_no|id) +
                    (1|item), 
                  data = trimmed_data_si_only_literal,
                  REML = FALSE)

lmer_si.1 <- lmer(pictureRT ~ 1 +
                    (1+yes_no|id) +
                    (1|item), 
                  data = trimmed_data_si_only_literal,
                  REML = FALSE)

anova(lmer_si.0,lmer_si.1)

summary(lmer_si.0)

save(esq_acc_m1.4,esq_psp_m1.1,esq_aris_acc_m1.0,esq_comp_acc_m1.0,fc_psp_m1.0,si_acc_m1.0,lmer_fc_zero_model.0,lmer_fc_zero_model.1,fc_acc_m1.0,lmer_esq_comp.0, lmer_esq_aris.0,
     lmer_esq.0,lmer_fc.1,lmer_si.0,lmer_si.1,
     file="glmer_esq_new.RData")
```

#Comparison response RT effect of distributivity inferences vs. scalar inferences

```{r}
as.factor(trimmed_data_selection$experiment)
as.factor(trimmed_data_selection$given_response)
droplevels(trimmed_data_selection$given_response)

#lmer analysis; use dummy coding of contrasts; ESQ controls as baseline; "ja, stimmt" as baseline for response
#experimental data/conditions in the analysis: ESQ every (true and false controls), 
#FC (neglect zero, yes vs. no responses), SI (imp false model, yes vs. no responses)

lmer_response_polarity_effect.0 <- lmer(pictureRT ~ experiment*given_response +
                    (1+experiment+given_response|id) +
                    (1|item), 
                  data = trimmed_data_selection,
                  REML = FALSE)

summary(lmer_response_polarity_effect.0)

lmer_response_polarity_effect.1 <- lmer(pictureRT ~ experiment+given_response +
                    (1+experiment+given_response|id) +
                    (1|item), 
                  data = trimmed_data_selection,
                  REML = FALSE)

anova(lmer_response_polarity_effect.0,lmer_response_polarity_effect.1)

#further investigate interaction in subset analyses
#ESQ vs. FC; no interaction with response polarity

trimmed_data_selection_esq_fc <- subset(trimmed_data_selection, trimmed_data_selection$experiment != "SI")

lmer_response_polarity_effect_esq_fc.0 <- lmer(pictureRT ~ experiment*given_response +
                    (1+experiment+given_response|id) +
                    (1|item), 
                  data = trimmed_data_selection_esq_fc,
                  REML = FALSE)

summary(lmer_response_polarity_effect_esq_fc.0)

lmer_response_polarity_effect_esq_fc.1 <- lmer(pictureRT ~ experiment+given_response +
                    (1+experiment+given_response|id) +
                    (1|item), 
                  data = trimmed_data_selection_esq_fc,
                  REML = FALSE)

anova(lmer_response_polarity_effect_esq_fc.0,lmer_response_polarity_effect_esq_fc.1)
#ESQ vs. SI; interaction with response polarity

trimmed_data_selection_esq_si <- subset(trimmed_data_selection, trimmed_data_selection$experiment != "FC")

lmer_response_polarity_effect_esq_si.0 <- lmer(pictureRT ~ experiment*given_response +
                    (1+experiment+given_response|id) +
                    (1|item), 
                  data = trimmed_data_selection_esq_si,
                  REML = FALSE)

summary(lmer_response_polarity_effect_esq_si.0)

lmer_response_polarity_effect_esq_si.1 <- lmer(pictureRT ~ experiment+given_response +
                    (1+experiment+given_response|id) +
                    (1|item), 
                  data = trimmed_data_selection_esq_si,
                  REML = FALSE)

anova(lmer_response_polarity_effect_esq_si.0,lmer_response_polarity_effect_esq_si.1)

save(esq_acc_m1.4,esq_psp_m1.1,esq_aris_acc_m1.0,esq_comp_acc_m1.0,fc_psp_m1.0,si_acc_m1.0,lmer_fc_zero_model.0,lmer_fc_zero_model.1,fc_acc_m1.0,lmer_esq_comp.0, lmer_esq_aris.0,
     lmer_esq.0,lmer_fc.1,lmer_si.0,lmer_si.1,lmer_response_polarity_effect.0,lmer_response_polarity_effect_esq_fc.0,lmer_response_polarity_effect_esq_si.0,
     file="glmer_esq_new.RData")
```