---
title: "Preprocessing of the experimental data reported in *Neglect-Zero effects in the interpretation of quantifiers and disjunction*"
author: "Oliver Bott, Fabian Schlotterbeck, Tomasz Klochowicz, Sonia Ramotowska & Maria Aloni"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(cli)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(trimr)
library(lme4)
library(lmerTest)
library(sjPlot)
library(dplyr)
library(ggbreak)
library(Rmisc)
library(reshape2)
library(stringr)
library(rlang)
library(naniar)
library(LMERConvenienceFunctions)
library(betareg)
library(performance)
library(forcats)

```

# Preprocessing 
## Import data from .csv
```{r}
rm(list=ls())
source("sdTrimBugFixed.R")

plots_dir<- file.path(getwd(),"plots")
if(!dir.exists(plots_dir)) dir.create(plots_dir, recursive = TRUE, showWarnings = FALSE)

subj_info <- read.csv(file = file.path("..", "data", "hohenentringen_subj_info.csv"))
data <- read.csv(file = file.path("..", "data", "hohenentringen.csv"))

```

## Some basic information about data
### Show how many pps
```{r}
sum(xtabs(~id, data=data)/205)
```
### Show how many trials each pp has done
```{r}
xtabs(~id, data)
```
### Show more stuff
```{r, results='hide'}
round(xtabs(~condition,data))
xtabs(~id+list, data=data)
xtabs(~item+condition, data=data)
```
### Prepare pp exclusion
```{r}
exclude <- NULL
```

### Show missing reading times
```{r}
xtabs(~data$time.out=="1",data)
```
<!-- ### Take a closer look at missing data -->
<!-- ```{r} -->
<!-- xtabs(~data$participant_id[which(data$time.out=="1")], data) -->

<!-- ### Exclude participants -->
<!-- ```{r} -->
<!-- exclude <- ... -->
<!-- ``` -->
### Mark all time out data as NA
```{r}
data$pictureRT[which(data$time.out=="1")] <- NA
xtabs(~is.na(data$pictureRT),data)
```
### Remove trials with NA values in pic rt
```{r}
data <- subset(data, !is.na(data$pictureRT))
# nrow(subset(data, is.na(data$id)))
# data <- subset(data, !is.na(data$id))
```
### Show average duration for experiments
```{r}
hist(subj_info$time_in_minutes, main = "Duration of experiments", xlab = "processing time in mins")
mean(subj_info$time_in_minutes) # N = 19.7
sd(subj_info$time_in_minutes)   # SD = 7.8
```
### Show pps more than three SD away from mean and add them to exclude list
```{r}
distance <- 3
x <- mean(subj_info$time_in_minutes) + distance * sd(subj_info$time_in_minutes)
y <- mean(subj_info$time_in_minutes) - distance * sd(subj_info$time_in_minutes)
filter(subj_info, time_in_minutes < y | time_in_minutes > x)
(exclude <- append(exclude, filter(subj_info, time_in_minutes < y | time_in_minutes > x)$id))

```
### Show missing reading times
```{r}
sort(tapply(data$ordered_responses, c(data$response_order), first))
#data$given_response <- ""
data$given_response <- case_when(data$response==37 ~ case_when(data$response_order %in% c(1,2)
                                                             ~ "ja, stimmt",
                                                             data$response_order %in% c(3,4)
                                                             ~ "nein, stimmt nicht",
                                                             data$response_order %in% c(5,6)
                                                             ~ "komische Frage"),
                                    data$response==40 ~ case_when(data$response_order %in% c(5,3)
                                                             ~ "ja, stimmt",
                                                             data$response_order %in% c(1,6)
                                                             ~ "nein, stimmt nicht",
                                                             data$response_order %in% c(2,4)
                                                             ~ "komische Frage"),
                                    data$response==39 ~ case_when(data$response_order %in% c(4,6)
                                                             ~ "ja, stimmt",
                                                             data$response_order %in% c(2,5)
                                                             ~ "nein, stimmt nicht",
                                                             data$response_order %in% c(1,3)
                                                             ~ "komische Frage"))
data$accuracy <- NULL
data$accuracy <- ifelse(tolower(data$given_response) == tolower(data$expected_response), 1, 0)
check_response_coding<-data[,c("response","ordered_responses","given_response","expected_response","accuracy")]
```

### Histogram of accuracy In (real) fillers (items 1000+) and/or 'homogeneity' items correctly
```{r}
data$item <- as.numeric(data$item)
#attention_controls <- data[data$item >= 1000,]#|| 
attention_controls <- data[(data$item>= 200 & data$item < 300 & data$condition %in% c(1,2,4)),]


control_accuracy<-aggregate(attention_controls$accuracy,list(attention_controls$id),mean,na.rm=TRUE)
names(control_accuracy)<- c("id","accuracy")

hist(control_accuracy$accuracy, main = "Frequency of percentages of false judgements in verification trials", xlab = "percentage of false judgements")
```

### Show how many pps are excluded under a given cut-off of 80%
```{r}
sum(control_accuracy$accuracy>=.8)
sum(control_accuracy$accuracy<.8)
(exclude <- append(exclude, control_accuracy[control_accuracy$accuracy<.8,]$id))
```

### Identify and exclude trials with extremely long reading times
```{r}
#melt_data_read <- subset(melt_data, roi!= "pictureRT" & !is.na(melt_data$rt))
#with(melt_data_read, plot(rt, col=participant_id))
data$read_time<-as.numeric(str_sub(data$read_time,2,-2))
cutoff_ex_rt <- 10000
data$extreme_read_time <- ifelse(data$read_time>cutoff_ex_rt,1,0)
aggregate(data$extreme_read_time,list(data$id),mean,na.rm=T)
#Sine no pp has extreme reading times in more than 5% of the trials and they are distributed evenly across conditions in the most extreme pp, we only exclude these individual trials instead of all the data from those pps
#TODO: exclude >5%
filtered_data <- subset(data, data$read_time<=cutoff_ex_rt)

```

### Remove excluded pps 
```{r}
filtered_data <- subset(filtered_data, !(id %in% exclude))
```
### Check how many pps remained
```{r}
length(unique(filtered_data$id))
```


### Use trimr to trim picture rt
```{r}
trimmed_data <- filtered_data

trimmed_data$cond <- trimmed_data$condition
trimmed_data$acc <- trimmed_data$accuracy

trimmed_data$pictureRT <- as.numeric(trimmed_data$pictureRT)
trimmed_data$rt = trimmed_data$pictureRT
trimmed_data$participant <- trimmed_data$id
trimmed_data$condition <- as.factor(paste(trimmed_data$experiment))
trimmed_data$accuracy <- 1 #(accuracy only because trimr needs this colmun name to function)


trimmed_data <- sdTrimBugFixed(data = trimmed_data, minRT = 200, sd = 3, 
                       perCondition = TRUE, perParticipant = TRUE,
                       omitErrors = FALSE, returnType = "raw", digits = 0)

hist(trimmed_data$rt)
range(trimmed_data$rt)
hist(trimmed_data$pictureRT)
range(trimmed_data$pictureRT)


trimmed_data$condition <- trimmed_data$cond
trimmed_data$accuracy <- trimmed_data$acc
```

### Convert to factor
```{r}
trimmed_data$id <- droplevels(as.factor(trimmed_data$id))
```



### Subset experiment and filler items 
```{r}
trimmed_data_esq <- subset(trimmed_data, experiment == "ES_Q")
trimmed_data_fc <- subset(trimmed_data, experiment == "FC")
trimmed_data_hom <- subset(trimmed_data, experiment == "Homogeneity") # additional experiment, included as fillers; all plots commented out
trimmed_data_si <- subset(trimmed_data, experiment == "SI")
trimmed_data_upto <- subset(trimmed_data, experiment == "Up_to")
trimmed_data_fillers <- subset(trimmed_data, experiment == "Filler")


```

## Exp1
### Name quantifiers, models, etc. and recombine data frames 
```{r}
###ESQ
trimmed_data_esq$quantifier = case_when(trimmed_data_esq$condition %in% c(1,2,3,4) ~ "less",
                                        trimmed_data_esq$condition %in% c(5,6,7,8) ~ "more",
                                        trimmed_data_esq$condition %in% c(9,10,11,12) ~ "every",
                                        trimmed_data_esq$condition %in% c(13,14,15,16) ~ "no")

trimmed_data_esq$model = case_when(trimmed_data_esq$condition %in% c(1,5,9,13) ~ "psp",
                                   trimmed_data_esq$condition %in% c(2,6,10,14) ~ "empty_set",
                                   trimmed_data_esq$condition %in% c(3,8,12) ~ "true",
                                   trimmed_data_esq$condition %in% c(4,7,11,15,16) ~ "false")

trimmed_data_esq$q_type = case_when(trimmed_data_esq$condition %in% 1:8 ~ "comparative",
                                    trimmed_data_esq$condition %in% 9:16 ~ "aristotelean")

trimmed_data_esq$mono = case_when(trimmed_data_esq$condition %in% c(1:4,13:16) ~ "down",
                                  trimmed_data_esq$condition %in% c(5:8,9:12) ~ "up")


###DIST
trimmed_data_fc$model = case_when(trimmed_data_fc$condition %in% c(1,5) ~ "psp",
                                  trimmed_data_fc$condition %in% c(2,6) ~ "empty_set",
                                  trimmed_data_fc$condition %in% c(3,7) ~ "true",
                                  trimmed_data_fc$condition %in% c(4,8) ~ "false")

trimmed_data_fc$disj_order = case_when(trimmed_data_fc$condition %in% 1:4 ~ "left",
                                       trimmed_data_fc$condition %in% 5:8 ~ "right")

##SI
trimmed_data_si$model = case_when(trimmed_data_si$condition %in% c(1) ~ "implicature",
                                  trimmed_data_si$condition %in% c(2) ~ "literal")

##Homogeneity
trimmed_data_hom$model = case_when(trimmed_data_hom$condition %in% c(1) ~ "psp",
                                   trimmed_data_hom$condition %in% c(4) ~ "true",
                                   trimmed_data_hom$condition %in% c(3) ~ "inhom",
                                   trimmed_data_hom$condition %in% c(2) ~ "false")

```






### Generate plots for accuracy (always relative to logical responses)
```{r}
plot_fc_acc <- ggplot(trimmed_data_fc, aes(y=accuracy, x=model, color=disj_order)) +
  stat_summary(fun = mean,
               geom = "pointrange",
               fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
               fun.min = function(x) mean(x) - sd(x)/sqrt(length(x))) + 
  scale_y_continuous(labels = scales::percent) +
  theme(text = element_text(size = 15)) + 
  ylab("mean logical responses (+/- 1 SEM)") + 
  scale_x_discrete(breaks=c("empty_set","false", "psp","true"),
                   labels=c("zero","false", "psp","true")) +
  scale_colour_discrete(labels = c("C-1 or C-2", "C-2 or C-1")) +
  theme(text = element_text(size = 15))  + labs(colour = "disj. order")
  

plot_fc_acc

ggsave(file.path(plots_dir,"plot_dist_acc.pdf"), width = 7, height = 7)
ggsave(file.path(plots_dir,"plot_dist_acc.png"), width = 7, height = 7)

plot_fc_acc_simp <- ggplot(trimmed_data_fc, aes(y=accuracy, x=model)) +
  stat_summary(fun = mean,
               geom = "pointrange",
               fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
               fun.min = function(x) mean(x) - sd(x)/sqrt(length(x))) + 
  scale_y_continuous(labels = scales::percent) +
  theme(text = element_text(size = 15)) + 
  ylab("mean logical responses (+/- 1 SEM)") + 
  scale_x_discrete(breaks=c("empty_set","false", "psp","true"),
                   labels=c("zero","false", "psp","true"))  +
  theme(text = element_text(size = 15))
  

plot_fc_acc_simp

ggsave(file.path(plots_dir,"plot_dist_acc_simp.pdf"), width = 7, height = 7)
ggsave(file.path(plots_dir,"plot_dist_acc_simp.png"), width = 7, height = 7)

trimmed_data_esq$quantifier <- factor(trimmed_data_esq$quantifier, levels = c("less", "more", "no", "every"), labels = c("less than n", "more than n", "no", "every"))

plot_esq_acc <- ggplot(trimmed_data_esq, aes(y=accuracy, x=model, colour = quantifier)) +
  stat_summary(fun = mean,
               geom = "pointrange",
               fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
               fun.min = function(x) mean(x) - sd(x)/sqrt(length(x))) + 
  scale_y_continuous(labels = scales::percent) + 
  theme(text = element_text(size = 15)) + 
  ylab("mean logical responses (+/- 1 SEM)") + 
  scale_x_discrete(breaks=c("empty_set","false", "psp","true"),
                   labels=c("zero","false", "psp","true")) 

plot_esq_acc

ggsave(file.path(plots_dir,"plot_esq_acc.pdf"), width = 7, height = 7)
ggsave(file.path(plots_dir,"plot_esq_acc.png"), width = 7, height = 7)

plot_si_acc <- ggplot(trimmed_data_si, aes(y=accuracy, x=model)) +
  stat_summary(fun = mean,
               geom = "pointrange",
               fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
               fun.min = function(x) mean(x) - sd(x)/sqrt(length(x))) +
  scale_y_continuous(labels = scales::percent) +
  theme(text = element_text(size = 15)) + 
  ylab("mean logical responses (+/- 1 SEM)") + 
  scale_x_discrete(breaks=c("implicature","literal"),
                   labels=c("lit: true, imp: true","lit: true, imp: false")) 

plot_si_acc

ggsave(file.path(plots_dir,"plot_si_acc.pdf"), width = 4, height = 7)
ggsave(file.path(plots_dir,"plot_si_acc.png"), width = 4, height = 7)

#plot_hom_acc <- ggplot(trimmed_data_hom, aes(y=accuracy, x=model)) +
#  stat_summary(fun = mean,
#               geom = "pointrange",
#               fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
#               fun.min = function(x) mean(x) - sd(x)/sqrt(length(x))) + 
#  scale_y_continuous(labels = scales::percent) + 
#  theme(text = element_text(size = 15)) + 
#  ylab("mean logical responses (+/- 1 SEM)")

#plot_hom_acc

#ggsave(file.path(plots_dir,"plot_hom_acc.pdf"), width = 7, height = 7)
#ggsave(file.path(plots_dir,"plot_hom_acc.png"), width = 7, height = 7)
```

# Stacked bar charts showing all three responses

```{r}
# stacked bar chart for FC
trimmed_data_fc$given_response <- as.factor(trimmed_data_fc$given_response)

stacked_fc <- trimmed_data_fc %>%
  mutate(model = fct_relevel(model, 
              "psp", "empty_set",  "true", "false")) %>%
  mutate(given_response = fct_relevel(given_response, 
              "nein, stimmt nicht", "ja, stimmt",  "komische Frage")) %>%
  mutate(quantifier='or') %>%
  ggplot(aes(x = model, fill = given_response)) +
  geom_bar(position = "fill", stat = "count") + scale_y_continuous(labels = scales::percent) + 
  scale_x_discrete(guide = guide_axis(n.dodge = 2),
                   breaks=c("psp","empty_set", "true","false"),
                   labels=c("Emp Restr.","DIST-viol", "True Ctrl.","False Ctrl.")) + 
  
  geom_text(size=15,aes(label = paste0("n=", after_stat(count))), stat='count', position = position_fill(vjust = 0.5)) + 
  theme_classic() +
  theme(text = element_text(size = 50)) +
  theme(legend.position = 'none')+
  theme(axis.title.y=element_blank(), axis.text.y=element_blank(), axis.title.x=element_blank())+
  scale_fill_discrete(labels = c("no, incorrect", "yes, correct", "weird question")) +
  labs(fill = "Response") +  
  facet_grid(~quantifier)

stacked_fc

ggsave(file.path(plots_dir,"stacked_dist.pdf"), width = 8, height = 15)
ggsave(file.path(plots_dir,"stacked_dist.png"), width = 8, height = 15)


# stacked bar chart for Homogeneity
#trimmed_data_hom$given_response <- as.factor(trimmed_data_hom$given_response)

#stacked_hom <- trimmed_data_hom %>%
#  mutate(given_response = fct_relevel(given_response, 
#              "nein, stimmt nicht", "ja, stimmt",  "komische Frage")) %>%
#  ggplot(aes(x = model, fill = given_response)) +
#  geom_bar(position = "fill", stat = "count") + scale_y_continuous(labels = scales::percent) + 
#  ylab("distributions of answers") +
#  geom_text(aes(label = paste0("n=", after_stat(count))), stat='count', position = position_fill(vjust = 0.5)) +
#  theme_classic()+
#  theme(text = element_text(size = 35)) +
#  scale_fill_discrete(labels = c("no, incorrect", "yes, correct", "weird question")) +
#  labs(fill = "Response") 

#stacked_hom

#ggsave(file.path(plots_dir,"stacked_hom.pdf"), width = 12, height = 7)
#ggsave(file.path(plots_dir,"stacked_hom.png"), width = 12, height = 7)
```

##change figure width for facet grid and ESQ

```{r}

# stacked bar chart for ESQ
trimmed_data_esq$given_response <- as.factor(trimmed_data_esq$given_response)

stacked_esq <- trimmed_data_esq %>%
  mutate(model = fct_relevel(model, 
              "psp", "empty_set",  "true", "false")) %>%
  mutate(given_response = fct_relevel(given_response, 
              "nein, stimmt nicht", "ja, stimmt",  "komische Frage"))  %>%
  ggplot(aes(x = model, fill = given_response)) +
  geom_bar(position = "fill", stat = "count") + scale_y_continuous(labels = scales::percent) + ylab("rel. frequencies of answers") +
  geom_text(size=15,aes(label = paste0("n=", after_stat(count))), stat='count', position = position_fill(vjust = 0.5)) +
  theme_classic() +
  theme(text = element_text(size = 50)) + 
  scale_x_discrete(guide = guide_axis(n.dodge = 2), 
                   breaks=c("psp", "empty_set",  "true", "false"),
                   labels=c("Empty Restr.","Empty Scope", "True Ctrl.","False Ctrl."))  +
  scale_fill_discrete(labels = c("no, incorrect", "yes, correct", "odd question")) +
  theme(text = element_text(size = 50),axis.title.x=element_blank()) + 
  theme(legend.position = 'none')+
  labs(fill = "Response") +
  facet_grid(~ quantifier)

stacked_esq

ggsave(file.path(plots_dir,"stacked_esq.pdf"), width = 36, height = 15)
ggsave(file.path(plots_dir,"stacked_esq.png"), width = 36, height = 15)

```

#adjust figure width for SI

```{r}
# stacked bar chart for SI

trimmed_data_si$given_response <- as.factor(trimmed_data_si$given_response)

stacked_si <- trimmed_data_si %>%
  mutate(given_response = fct_relevel(given_response, 
              "nein, stimmt nicht", "ja, stimmt",  "komische Frage")) %>%
  ggplot(aes(x = model, fill = given_response)) +
  geom_bar(position = "fill", stat = "count") + scale_y_continuous(labels = scales::percent) + ylab("distributions of answers") +
  geom_text(aes(label = paste0("n=", after_stat(count))), stat='count', position = position_fill(vjust = 0.5)) +
  scale_x_discrete(breaks=c("implicature","literal"),
                   labels=c("lit: true, imp: true","lit: true, imp: false"))  +
  theme_classic() +
  theme(text = element_text(size = 18)) +
  scale_fill_discrete(labels = c("no, incorrect", "yes, correct", "weird question")) +
  theme(text = element_text(size = 15)) + 
  labs(fill = "Response") 

stacked_si

ggsave(file.path(plots_dir,"stacked_si.pdf"))
ggsave(file.path(plots_dir,"stacked_si.png"))

```


## Encode
### Encode legit responses 
```{r}
###ESQ
trimmed_data_esq$legit_responses_one = case_when(trimmed_data_esq$condition %in% c(2,3,8,12,14)
                                             ~ case_when(tolower(trimmed_data_esq$given_response)
                                                         == tolower("ja, stimmt") ~ TRUE,
                                                         .default = FALSE),
                                             trimmed_data_esq$condition %in% c(1,5,9,13)
                                             ~ case_when(tolower(trimmed_data_esq$given_response)
                                                         == tolower("komische Frage") ~ TRUE,
                                                         .default = FALSE),
                                             .default=FALSE)

trimmed_data_esq$legit_responses_two = case_when(trimmed_data_esq$condition
                                                 %in% c(2,4,6,7,10,11,14,16,15)
                                                 ~ case_when(tolower(trimmed_data_esq$given_response)
                                                             == tolower("nein, stimmt nicht") ~ TRUE,
                                                             .default = FALSE),
                                                 .default = FALSE)



###DIST
trimmed_data_fc$legit_responses_one = case_when(trimmed_data_fc$condition %in% c(2,3,6,7)
                                             ~ case_when(tolower(trimmed_data_fc$given_response)
                                                         == tolower("ja, stimmt") ~ TRUE,
                                                         .default = FALSE),
                                             trimmed_data_fc$condition %in% c(1,5)
                                             ~ case_when(tolower(trimmed_data_fc$given_response)
                                                         == tolower("komische Frage") ~ TRUE,
                                                         .default = FALSE),
                                             .default=FALSE)

trimmed_data_fc$legit_responses_two = case_when(trimmed_data_fc$condition
                                                 %in% c(2,6,4,8)
                                                 ~ case_when(tolower(trimmed_data_fc$given_response)
                                                             == tolower("nein, stimmt nicht") ~ TRUE,
                                                             .default = FALSE),
                                                 .default = FALSE)


###SI
trimmed_data_si$legit_responses_one = case_when(trimmed_data_si$condition %in% c(1,2)
                                             ~ case_when(tolower(trimmed_data_si$given_response)
                                                         == tolower("ja, stimmt") ~ TRUE,
                                                         .default = FALSE),
                                             .default=FALSE)

trimmed_data_si$legit_responses_two = case_when(trimmed_data_si$condition
                                                 %in% c(2)
                                                 ~ case_when(tolower(trimmed_data_si$given_response)
                                                             == tolower("nein, stimmt nicht") ~ TRUE,
                                                             .default = FALSE),
                                                 .default = FALSE)



```




### Subset to legit responses 
```{r}
###ESQ
trimmed_data_esq_legit <- subset(trimmed_data_esq, trimmed_data_esq$legit_responses_one | trimmed_data_esq$legit_responses_two)

###DIST
trimmed_data_fc_legit <- subset(trimmed_data_fc, trimmed_data_fc$legit_responses_one | trimmed_data_fc$legit_responses_two)

###SI
trimmed_data_si_legit <- subset(trimmed_data_si, trimmed_data_si$legit_responses_one | trimmed_data_si$legit_responses_two)


```


### Plot RT of legit responses 
```{r}
###ESQ
plot_esq_rt_legit <- trimmed_data_esq_legit  %>%
  mutate(model = fct_relevel(model, 
              "psp", "empty_set",  "true", "false")) %>%
  mutate(given_response = fct_relevel(given_response, 
              "nein, stimmt nicht", "ja, stimmt",  "komische Frage"))  %>%
  ggplot(aes(y=pictureRT, x=model, colour = given_response)) +
  stat_summary(fun = mean,
               geom = "pointrange",
               fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
               fun.min = function(x) mean(x) - sd(x)/sqrt(length(x))) + 
  #scale_y_continuous(labels = scales::percent) + 
  ylab("mean RT in ms. (+/- 1 SEM)") +
   scale_x_discrete(breaks=c("psp", "empty_set",  "true", "false"),
                   labels=c("Empty Restr.","Empty Scope", "True Ctrl.","False Ctrl."))  +
  scale_colour_discrete(labels = c("no, incorrect", "yes, correct", "weird question")) +
   
  facet_grid(~ quantifier) +
  theme(text = element_text(size = 22), axis.title.x=element_blank(), axis.text.x = element_text(angle = 60, vjust = 1, hjust=1)) + 
  theme(legend.position = 'none')+
  coord_cartesian(ylim = c(1000, 2300))+
  labs(colour = "Response") 
  
  

plot_esq_rt_legit

ggsave(file.path(plots_dir,"plot_esq_rt_legit.pdf"), width = 12, height = 6)
ggsave(file.path(plots_dir,"plot_esq_rt_legit.png"), width = 12, height = 6)



###DIST
plot_fc_rt_legit <- trimmed_data_fc_legit  %>%
  mutate(quantifier='or') %>%
    mutate(given_response = fct_relevel(given_response, 
              "nein, stimmt nicht", "ja, stimmt",  "komische Frage"))  %>%
  mutate(model = fct_relevel(model, 
              "psp", "empty_set",  "true", "false")) %>%
  ggplot( aes(y=pictureRT, x=model, colour = given_response)) + stat_summary(fun = mean,
               geom = "pointrange",
               fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
               fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)))+
  #scale_y_continuous(labels = scales::percent) + 
  ylab("mean RT in ms. (+/- 1 SEM)") +
 scale_x_discrete(breaks=c("psp", "empty_set",  "true", "false"),
                   labels=c("Emp Restr.","DIST-viol", "True Ctrl.","False Ctrl."))  +
  scale_colour_discrete(labels = c("no, incorrect", "yes, correct", "weird question")) +
       theme(legend.position = 'none')+
  theme(text = element_text(size = 22))  + 
   facet_grid(~ quantifier) +
  theme(axis.title.y=element_blank(), axis.text.y=element_blank(),axis.title.x=element_blank(),axis.text.x = element_text(angle = 60, vjust = 1, hjust=0.85))+
  coord_cartesian(ylim = c(1000, 2300))+
  labs(colour = "Response")

plot_fc_rt_legit

#ggsave(file.path(plots_dir,"plot_fc_rt_legit.pdf"), width = 4, height = 5)
#ggsave(file.path(plots_dir,"plot_fc_rt_legit.png"), width = 4, height = 5)
ggsave(file.path(plots_dir,"plot_dist_rt_legit_wo.pdf"), width = 3, height = 6)
ggsave(file.path(plots_dir,"plot_dist_rt_legit_wo.png"), width = 3, height = 6)

plot_fc_rt <- ggplot(trimmed_data_fc, aes(y=pictureRT, x=model, colour = given_response)) + stat_summary(fun = mean,
               geom = "pointrange",
               fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
               fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)))+
  #scale_y_continuous(labels = scales::percent) + 
  ylab("mean RT in ms. (+/- 1 SEM)") +
    scale_x_discrete(breaks=c("empty_set","false", "psp","true"),
                   labels=c("zero","false", "psp","true")) +
  scale_colour_discrete(labels = c("yes, correct", "weird question", "no, incorrect")) +
 
  theme(text = element_text(size = 15)) 

plot_fc_rt

ggsave(file.path(plots_dir,"plot_dist_rt.pdf"))
ggsave(file.path(plots_dir,"plot_dist_rt.png"))

plot_si_rt_legit <- trimmed_data_si_legit  %>%
  mutate(model = fct_relevel(model, 
              "psp", "empty_set",  "true", "false")) %>% ggplot(aes(y=pictureRT, x=model, colour = given_response)) + stat_summary(fun = mean,
               geom = "pointrange",
               fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
               fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)))+
  #scale_y_continuous(labels = scales::percent) + 
  ylab("mean RT in ms. (+/- 1 SEM)") +
  #scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_x_discrete(breaks=c("implicature", "literal"),
                   labels=c("lit: true, imp: true", "lit: true, imp: false")) +
  scale_colour_discrete(labels = c("yes, correct", "no, incorrect")) +
  theme(text = element_text(size = 15)) + 
  labs(colour = "Response") 

plot_si_rt_legit

ggsave(file.path(plots_dir,"plot_si_rt_legit.pdf"))
ggsave(file.path(plots_dir,"plot_si_rt_legit.png"))


```

#Merge data for comparison between response polarity effects of distributivity vs scalar implicature inferences

Comparison within UE Aristotelean quantifiers. Include control conditions for *every* from ESQ subexperiment as baseline comparisons.

```{r}
###ESQ
trimmed_data_esq$selection_responses_one = case_when(trimmed_data_esq$condition %in% c(12)
                                             ~ case_when(tolower(trimmed_data_esq$given_response)
                                                         == tolower("ja, stimmt") ~ TRUE,
                                                         .default = FALSE),
                                             .default=FALSE)

trimmed_data_esq$selection_responses_two = case_when(trimmed_data_esq$condition
                                                 %in% c(11)
                                                 ~ case_when(tolower(trimmed_data_esq$given_response)
                                                             == tolower("nein, stimmt nicht") ~ TRUE,
                                                             .default = FALSE),
                                                 .default = FALSE)

###FC
trimmed_data_fc$selection_responses_one = case_when(trimmed_data_fc$condition %in% c(2,6)
                                             ~ case_when(tolower(trimmed_data_fc$given_response)
                                                         == tolower("ja, stimmt") ~ TRUE,
                                                         .default = FALSE),
                                             .default=FALSE)

trimmed_data_fc$selection_responses_two = case_when(trimmed_data_fc$condition
                                                 %in% c(2,6)
                                                 ~ case_when(tolower(trimmed_data_fc$given_response)
                                                             == tolower("nein, stimmt nicht") ~ TRUE,
                                                             .default = FALSE),
                                                 .default = FALSE)

###SI
trimmed_data_si$selection_responses_one = case_when(trimmed_data_si$condition %in% c(2)
                                             ~ case_when(tolower(trimmed_data_si$given_response)
                                                         == tolower("ja, stimmt") ~ TRUE,
                                                         .default = FALSE),
                                             .default=FALSE)

trimmed_data_si$selection_responses_two = case_when(trimmed_data_si$condition
                                                 %in% c(2)
                                                 ~ case_when(tolower(trimmed_data_si$given_response)
                                                             == tolower("nein, stimmt nicht") ~ TRUE,
                                                             .default = FALSE),
                                                 .default = FALSE)

###ESQ
trimmed_data_esq_selection <- subset(trimmed_data_esq, trimmed_data_esq$selection_responses_one | trimmed_data_esq$selection_responses_two)

###FC
trimmed_data_fc_selection <- subset(trimmed_data_fc, trimmed_data_fc$selection_responses_one | trimmed_data_fc$selection_responses_two)

###SI
trimmed_data_si_selection <- subset(trimmed_data_si, trimmed_data_si$selection_responses_one | trimmed_data_si$selection_responses_two)

###merge dataframes

df_list <- list(trimmed_data_esq_selection, trimmed_data_fc_selection, trimmed_data_si_selection)
trimmed_data_selection <- Reduce(function(x, y) merge(x, y, all=TRUE), df_list, accumulate=FALSE)

###plot RTs of all conditions in merged dataframe

plot_rt_selection <- trimmed_data_selection  %>%
   mutate(quantifier='polarity') %>%    
  mutate(given_response = fct_relevel(given_response, 
              "nein, stimmt nicht", "ja, stimmt",  "komische Frage"))  %>%
  ggplot(aes(y=pictureRT, x=experiment, colour = given_response)) +
  stat_summary(fun = mean,
               geom = "pointrange",
               fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
               fun.min = function(x) mean(x) - sd(x)/sqrt(length(x))) + 
  #scale_y_continuous(labels = scales::percent) + 
  ylab("mean RT in ms. (+/- 1 SEM)") +
  xlab("compared models") +
  scale_x_discrete(breaks=c("ES_Q","FC", "SI"),
                   labels=c("BASE (Exp. 1)","DIST (Exp. 2)", "UB (Exp. 3)")) +
  scale_colour_discrete(type= c("#F8766D", "#00BA38", "#619CFF"),labels = c("no, false","yes, true",  "weird question")) +
  labs(colour = "Response") +
  theme(text = element_text(size = 20))  + 
   facet_grid(~ quantifier) +
         theme(legend.position = 'none')+
  theme(axis.title.y=element_blank(), axis.text.y=element_blank(),axis.title.x=element_blank(), axis.text.x = element_text(angle = 60, vjust = 1, hjust=1))+
  coord_cartesian(ylim = c(1000, 2300))

plot_rt_selection
#ggsave(file.path(plots_dir,"plot_dist_vs_si_answer_polarity_effect.pdf"), width = 5, height = 5)
#ggsave(file.path(plots_dir,"plot_dist_vs_si_answer_polarity_effect.png"), width = 5, height = 5)
ggsave(file.path(plots_dir,"plot_dist_vs_si_answer_polarity_effect_wo.pdf"), width = 4, height = 6)
ggsave(file.path(plots_dir,"plot_dist_vs_si_answer_polarity_effect_wo.png"), width = 4, height = 6)
```

### Save all
```{r}
save(trimmed_data, trimmed_data_esq, trimmed_data_fc, trimmed_data_si, trimmed_data_hom, trimmed_data_upto, trimmed_data_fillers, trimmed_data_selection, file = "trimmedData.RData")
```





